\section{Introduction}

\subsection{The setting}

% slide
\begin{frame}{Who uses...}

\begin{itemize}
	\item We all use computers to generate or process data
\end{itemize}

Question to the audience: who uses...

\begin{columns}[t]

\column{0.5\textwidth}

\begin{itemize}
	\item C/C++?
	\item Fortran?
	\item Ada?
	\item Java?
	\item Matlab/Octave?
\end{itemize}

\column{0.5\textwidth}

\begin{itemize}
	\item IDL?
	\item Perl?
	\item Ruby?
	\item \alert{Python}?
\end{itemize}

\end{columns}

\end{frame}

% Slide
\begin{frame}{What is Python?}

Python is/has...

\begin{columns}[t]

\column{0.5\textwidth}

\begin{itemize}
	\item a scripting language
	\item general purpose
	\item interpreted
	\item easy to learn
	\item clean syntax
\end{itemize}

\column{0.5\textwidth}

\begin{itemize}
	\item multi-paradigm
	\item open-source
	\item available for all major platforms
	\item great community
\end{itemize}

\end{columns}

\end{frame}

\subsection{The best of all}


\begin{frame}{The best of all:}

\begin{exbox}{Python comes...}
	... with \alert{batteries included}!
\end{exbox}

\vspace{-1.25ex}

\begin{center}
	Libraries available for...
\end{center}

\vspace{-4.5ex}

\begin{columns}[t]

\column{0.3\textwidth}

\begin{center}
	daily IT needs...
\end{center}

\vspace{-2.5ex}

\begin{itemize}
	\item networks
	\item OS interaction
	\item temporary files
	\item zip files
	\item ...
\end{itemize}

\column{0.7\textwidth}

\begin{center}
	\alert{science!}
\end{center}

\vspace{-2.5ex}

\begin{itemize}
	\item efficient array operations (\emph{NumPy})
	\item general numerical algorithms (\emph{SciPy})
	\item 2D visualization (\emph{matplotlib})
	\item 3D visualization (Mayavi)
	\item special problems (e.g. finite elements with FEniCS, quantum optics with QuTiP)
	\item symbolic math (SageMath, sympy)
	\item ...
\end{itemize}

\end{columns}

\end{frame}

